Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy

### 2017-01-26 paper_draft.Rmd
removed mentions to appendix
github link
last digits only

---
title: "Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy"
author: "09688532 and 91455724"
date: "2017-01-26"
header-includes:
    - \usepackage{setspace}\doublespacing
output: pdf_document

@@

### Logistic Regression
We built a logistic regression model to predict the probability that one will have erectile function at two years after SBRT. The model was built in the R language version 3.3.2 (2016-10-31), using the package glm. See appendix XX for the full reproducible code document.

@@

>>>>

---
title: "Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy"
author: "8532 and 5724"
date: "2017-01-26"
header-includes:
    - \usepackage{setspace}\doublespacing
output: pdf_document

@@

### Logistic Regression
We built a logistic regression model to predict the probability that one will have erectile function at two years after SBRT. The model was built in the R language version 3.3.2 (2016-10-31), using the package glm.

@@

## Appendix
See our github at https://github.com/tzeriver/699 for all code and documents.
